\section{Discussion}
\subsection{Principal findings and relation to prior work}
The Conformer pipeline elevated macro-averaged discrimination while curbing false alarms compared with widely used CNN-LSTM and Transformer baselines, demonstrating that hybrid convolutional-attention blocks can unlock clinically meaningful gains without sacrificing interpretability. The attention maps localized aberrant depolarization patterns that align with electrophysiology heuristics, echoing recent reports of genetic-programming ensembles and saliency-guided ECG classifiers that foreground clinical reasoning.\cite{Czerwinski2025Interpretable,Gliner2025Interpretability} Moreover, the stability improvements on minority arrhythmias complement wearable-focused studies that inferred impending atrial fibrillation from noisier single-lead recordings, underscoring the value of context-aware representations when data acquisition conditions cannot be tightly controlled.\cite{Gadaleta2023SingleLead}

\subsection{Implications for telecardiology workflows}
By constraining alert volumes to 7.4\% of monitoring windows, the calibrated model satisfies operational targets derived from prospective trials of AI-enabled ECG surveillance and preserves clinician bandwidth for high-risk encounters.\cite{Hsieh2025Economic,Hempel2025ECGAging} Integrating structured explanations with scalar risk estimates also mirrors BioMedical Engineering OnLine deployments in rehabilitation and operating-room safety, where interpretable analytics facilitated interdisciplinary adoption.\cite{Yoon2023Interpretable,Stern2024InBed,Silva2023Infusion} The modular preprocessing and calibration stages allow straightforward adaptation to longer-term wearables or implantable loop recorders, while the open-source implementation adheres to BMC expectations for data and code availability.

\subsection{Limitations and future directions}
Despite the gains, residual errors on fusion beats reveal the need for targeted data augmentation and clinical adjudication to refine labels that are scarce even in curated repositories. Expanding the training corpus with synthetic signals or cross-dataset fine-tuning may mitigate these deficiencies but warrants caution to avoid distribution shift, as highlighted by BioMedical Engineering OnLine investigations into transferability across imaging and motion-tracking modalities.\cite{Chen2024SuperResolution,Sugiarto2025GroundReaction,Li2025Antioxidant} Future work will couple conformer-based feature extraction with probabilistic calibration layers and federated training schemes to align with privacy requirements in multi-center telehealth deployments. Additionally, collaborating with pediatric cardiology programs could illuminate age-specific feature dependencies analogous to those reported for pubertal sex estimation from ECGs.\cite{Osullivan2024Pediatric}

\subsection{Ethical considerations}
The study exclusively utilized de-identified public datasets, and all analytic code, trained weights, and derived attention summaries will be released alongside this manuscript to support independent verification. No human subjects were recruited, obviating the need for institutional review, and the analytical workflow complies with the project’s documented ethics and data availability statements.
